\documentclass{article}
\usepackage{amsmath}

\title{Summary of Tests and Equations for Series and Sequences}
\author{}
\date{}

\begin{document}

\maketitle

\section*{1. Basic Definitions}

\begin{itemize}
    \item \textbf{Sequence Convergence}: A sequence $\{a_n\}$ converges to $L$ if $\lim_{n \to \infty} a_n = L$.
    \item \textbf{Series Convergence}: The series $\sum a_n$ converges if the partial sums $S_n = \sum_{k=1}^n a_k$ approach a finite limit as $n \to \infty$.
\end{itemize}

\section*{2. Tests for Series Convergence and Divergence}

\subsection*{Divergence Test (Test for Divergence)}
If $\lim_{n \to \infty} a_n \neq 0$, then the series $\sum a_n$ \textbf{diverges}. If $\lim_{n \to \infty} a_n = 0$, this test is inconclusive.

\subsection*{Geometric Series Test}
For a series $\sum ar^n$, it converges if $|r| < 1$ and diverges if $|r| \geq 1$.
\begin{itemize}
    \item \textbf{Sum for a convergent geometric series}: $S = \frac{a}{1 - r}$.
\end{itemize}

\subsection*{p-Series Test}
A p-series $\sum \frac{1}{n^p}$ converges if $p > 1$ and diverges if $p \leq 1$.

\subsection*{Comparison Test}
For $\sum a_n$ and a positive comparison series $\sum b_n$:
\begin{itemize}
    \item If $0 \leq a_n \leq b_n$ and $\sum b_n$ converges, then $\sum a_n$ converges.
    \item If $0 \leq b_n \leq a_n$ and $\sum b_n$ diverges, then $\sum a_n$ diverges.
\end{itemize}

\subsection*{Limit Comparison Test}
If $\lim_{n \to \infty} \frac{a_n}{b_n} = L$, where $0 < L < \infty$, then $\sum a_n$ and $\sum b_n$ both converge or diverge.

\subsection*{Ratio Test}
For a series $\sum a_n$, calculate $L = \lim_{n \to \infty} \left| \frac{a_{n+1}}{a_n} \right|$:
\begin{itemize}
    \item If $L < 1$, the series converges absolutely.
    \item If $L > 1$, the series diverges.
    \item If $L = 1$, the test is inconclusive.
\end{itemize}

\subsection*{Root Test}
For a series $\sum a_n$, calculate $L = \lim_{n \to \infty} \sqrt[n]{|a_n|}$:
\begin{itemize}
    \item If $L < 1$, the series converges absolutely.
    \item If $L > 1$, the series diverges.
    \item If $L = 1$, the test is inconclusive.
\end{itemize}

\subsection*{Alternating Series Test (Leibniz Test)}
For an alternating series $\sum (-1)^{n-1} b_n$:
\begin{itemize}
    \item The series converges if $b_n$ is decreasing and $\lim_{n \to \infty} b_n = 0$.
\end{itemize}

\section*{3. Absolute and Conditional Convergence}
\begin{itemize}
    \item \textbf{Absolute Convergence}: If $\sum |a_n|$ converges, then $\sum a_n$ converges absolutely.
    \item \textbf{Conditional Convergence}: If $\sum a_n$ converges but $\sum |a_n|$ diverges, then $\sum a_n$ converges conditionally.
\end{itemize}

\section*{4. Power Series}
A power series $\sum a_n x^n$ converges within its \textbf{radius of convergence} $R$.
\begin{itemize}
    \item \textbf{Interval of Convergence}: $( -R, R)$
    \item \textbf{Ratio Test for Radius}: $R = \lim_{n \to \infty} \left| \frac{a_n}{a_{n+1}} \right|$ if this limit exists.
\end{itemize}

\end{document}
